Public Opinions on Sexual Education in Public Schools

### 2024-03-19 paper/paper.qmd
Add related work in Ethics and Bias

The GSS upholds ethical standards by ensuring the anonymity and confidentiality of respondents, essential for ensuring honest responses. Participants are informed about their rights as respondents, and are assured that their participation is voluntary, with the option to withdraw at any time. These measures adhere to the ethical principles of respect for persons, beneficence, and justice, safeguarding the dignity and privacy of individuals while collecting data that could inform policy and educational content.

Despite these precautions, potential biases such as response bias may still influence the data. Respondents might alter their answers based on perceived social desirability or due to discomfort with discussing sexual education openly, leading to underreporting or overreporting of certain views. Acknowledging and addressing these biases is crucial for the integrity of the research process. Efforts to mitigate such biases include the careful design of survey questions, the use of neutral language, and the provision of a secure and respectful environment for data collection. Through vigilant attention to ethics and bias, the research strives to produce findings that are not only insightful but also respectful and representative of the population's diverse opinions on sexual education.

>>>>

The GSS upholds ethical standards by ensuring the anonymity and confidentiality of respondents, essential for ensuring honest responses. Participants are informed about their rights as respondents, and are assured that their participation is voluntary, with the option to withdraw at any time. These measures adhere to the ethical principles of respect for persons, beneficence, and justice, safeguarding the dignity and privacy of individuals while collecting data that could inform policy and educational content. @Woolweaver2022 emphasize the importance of inclusive and equitable sexual education, highlighting the harm and exclusion faced by marginalized student groups in current programs and proposing a shift towards more inclusive approaches

Despite these precautions, potential biases such as response bias may still influence the data. Respondents might alter their answers based on perceived social desirability or due to discomfort with discussing sexual education openly, leading to underreporting or overreporting of certain views. Acknowledging and addressing these biases is crucial for the integrity of the research process. Efforts to mitigate such biases include the careful design of survey questions, the use of neutral language, and the provision of a secure and respectful environment for data collection. @Lamb2010 critiques current sex education curricula for neglecting ethical dimensions and proposes teaching ethical reasoning to make sex education a form of citizenship education, thereby mitigating biases. Through vigilant attention to ethics and bias, the research strives to produce findings that are not only insightful but also respectful and representative of the population's diverse opinions on sexual education.
